\documentstyle[palatino,psfig,url]{article}
\setlength{\oddsidemargin}{0.25 in}
\setlength{\evensidemargin}{-0.25 in}
%%\setlength{\topmargin}{-0.6 in}
\setlength{\topmargin}{-0.95 in}
\setlength{\textwidth}{6.5 in}
%%\setlength{\textheight}{8.5 in}
%%%\setlength{\textheight}{9 in}
\setlength{\textheight}{10 in}
%%\setlength{\headsep}{0.55 in}
\setlength{\headsep}{0.35 in}
\setlength{\parindent}{0 in}
%%\setlength{\parskip}{0.1 in}
\setlength{\parskip}{0.01 in}


\addtolength{\evensidemargin}{-15pt}
\addtolength{\oddsidemargin}{-15pt}

\pagestyle{empty}

\begin{document}
\begin{center} \bf
\Large
                               Todd D. Hodes
\medskip
\normalsize


\begin{tabular}{lp{3in}r}
770 Santa Barbara Rd.  & & hodes@cs.berkeley.edu \\
Berkeley, CA  94707 & & www.cs.berkeley.edu/\url{~}hodes \\
(510)  524 - 4303 \\
\end{tabular}

\end{center}

\bigskip

%\begin{tabbing}
%xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx 
%\= \kill
%Permanent Address                                 \> Present Address \\
%770 Santa Barbara Rd.                             \> 770 Santa Barbara Rd. \\
%Berkeley, CA  94707                               \> Berkeley, CA  94707 \\
%(510)  524 - 4303                                 \> (510)  524 - 4303 \\
%hodes@cs.berkeley.edu     \\
%\end{tabbing}

\begin{bf} \large
Education \\[-18pt]
\end{bf}

\begin{tabbing}
xxi \= \kill
\>   Ph.\ D. in Computer Science, 2002 \\
\>   M.\ S. in  Computer Science, 1997 \\
\>   University of California, Berkeley \\
\>   GPA:  \, 3.95 \\
\smallskip \\[-6pt]
\>   B.\ S. in Computer Science, Applied Mathematics, high honors, 1994 \\
\>   University of Virginia \\
\>   GPA: \, Computer Science: 3.97, \, Applied Mathematics: 3.90, \, 
          Cumulative: 3.77 \\
\>   SAT: \, M: 800 V: 690, \, GRE: \, Q: 800 A: 800 V: 690, \, 
          CS subject: 840 (98\%)\\
\end{tabbing}


\begin{bf} \large
Honors, Awards, Achievements  \\[-16pt]
\end{bf}

\begin{itemize}
\item  Best Paper Award, 3rd ACM/IEEE International Conference on Mobile Computing, 1997 \\[-18pt]
\item  Member of University of Virginia Alumni Technology Committee \\[-18pt]
\item  California Fellowship in Microelectronics,
        University of California, Berkeley, 1994-1995 \\[-18pt]
\item  Louis T. Radar Award, U. Va. Computer Science Department, April 1994 \\[-18pt]
\item  Finalist, University of Virginia Research \& Design Competition, 
        April 1994 \\[-18pt]
\item  Dean's List, University of Virginia, 1990-1994 \\[-18pt]
\item  Intermediate Honors, University of Virginia, 1992 \\[-18pt]
\item  Tau Beta Pi honor society, 1991-1995 \\[-18pt]
\item  Golden Key honor society, 1992-1995 \\[-18pt]
\item  National Merit Scholar, 1990 \\[-18pt]
\item  American Computer Science League (ACSL) All-Star Contest, 
         Individual Competition:  \\[-18pt]
    \begin{itemize}
    \item{Tied for first place in division, 1990, Washington, DC} \\[-14pt]
    \item{Ranked in top ten in division, 1989, Toronto, Canada} \\[-18pt]
    \end{itemize}
\item    Duke University Summer Computing Program, Full Scholarship, 1987 \\
\end{itemize}


%%%%%% \newpage

\begin{bf} \large
Publications
\end{bf}
\begin{tabbing}
xxi \= xx \= x \= \kill
\>    T. Hodes, S. Czerwinski, B. Zhao, A. Joseph, R. H. Katz \\
\>\>      ``An Architecture for Secure Wide-area Service Discovery'' \\
\>\>       ACM Wireless Networks Journal, Special Issue \\
\>\>       Volume 8, Issue 2/3, March/May 2002, pp. 213-230 \\

\smallskip \\[-3pt]
\>   M. Munson, T. Hodes, T. Fischer, K. H. Lee, T. Lehman, B. Zhao \\
\>\>      ``Flexible Internetworking of Devices and Controls'' \\
\>\>        25th Annual Conference of the IEEE Industrial Electronics Society (IECON),  \\
\>\>	    San Jose, CA, December 1999. \\
\smallskip \\[-3pt]
\>    T. D. Hodes, R. H. Katz \\
\>\>      ``Composable Ad hoc Location-based Services for Heterogeneous
             Mobile Clients,'' \\
\>\>       ACM Wireless Networks Journal, Special issue on Mobile Computing \\
\>\>       Vol. 5, No. 5, October 1999, pp. 411-427. \\
\smallskip \\[-3pt]
\>    T. Hodes, R. H. Katz \\
\>\>      ``A Document-based Framework for Internet Application Control'' \\
\>\>       2nd USENIX Symposium on Internet Technologies and Systems \\
\>\>       Boulder, CO, October 1999, pp. 59-70. \\
\smallskip \\[-3pt]
\>    T. Hodes, J. Hauser, A. Freed, J. Wawrzynek\\
\>\>      ``Second-order Recursive Oscillators for Musical Additive Synthesis \\
\>\>\>        Applications on SIMD and VLIW Processors,'' \\
\>\>       International Computer Music Conference (ICMC), Beijing, China, October 1999. \\
\end{tabbing}
\newpage
\begin{bf} \large
Publications, cont.
\end{bf}
\begin{tabbing}
xxi \= xx \= x \= \kill
\>    S. Czerwinski, B. Zhao, T. Hodes, A. Joseph, R. H. Katz \\
\>\>      ``An Architecture for a Secure Service Discovery Service'' \\
\>\>       5th ACM/IEEE International Conference on Mobile Computing \\
\>\>       Seattle, WA, August 1999, pp. 24-35. \\
\smallskip \\[-3pt]
\>    Steven McCanne, Eric Brewer, Randy Katz, Elan Amir, Yatin Chawathe,
    Todd Hodes, et. al. \\
\>\>      ``MASH: Enabling Scalable Multipoint Collaboration'' \\
\>\>       ACM Computing Surveys, Volume 31, No. 2es, June 1999. \\
\smallskip \\[-3pt]
\>    T. Hodes, J. Hauser, A. Freed, J. Wawrzynek, D. Wessel \\
\>\>      ``A Fixed-point Recursive Digital Oscillator for Additive Synthesis
        of Audio,'' \\
\>\>       IEEE International Conference on Acoustics, Speech, and Signal
            Processing,  \\
\>\>        Phoenix, Arizona, March 1999. \\
\smallskip \\[-3pt]
\>    T. Hodes, M. Newman, S. McCanne, R. H. Katz, J. Landay \\
\>\>      ``Shared Remote Control of a Videoconferencing Application: 
            Motivation, Design, and Implementation,'' \\
\>\>       SPIE Multimedia Computing and Networking 1999,  \\
\>\>        San Jose, California, January 1999, pp. 17-28. \\
\smallskip \\[-3pt]
\>    E. Brewer, R. H. Katz, E. Amir, H. Balakrishnan, Y. Chawathe, A. Fox,
    S. Gribble, T. Hodes, G. Nguyen, \\
\>\>\> V. Padmanabhan, M. Stemm, S. Seshan, T. Henderson \\
\>\>      ``A Network Architecture for Heterogeneous Mobile Computing,'' \\
\>\>       IEEE Personal Communications Magazine, October 1998. Invited Paper. \\
\smallskip \\[-3pt]
\>    T. D. Hodes, R. H. Katz \\
\>\>      ``Enabling `Smart Spaces:' Entity Description and User Interface
        Generation \\
\>\>\>     for a Heterogeneous Component-Based Distributed System,'' \\
\>\>       DARPA/NIST Smart Spaces Workshop,  \\
\>\>       Gaithersburg, Maryland, July 1998.  pp. 7/44-7/51.  \\
\>\>       also, UC Berkeley Technical Report CSD/98/1008. \\
\smallskip \\[-3pt]
\>    T. D. Hodes, R. H. Katz, E. Servan-Schreiber, L. A. Rowe \\
\>\>      ``Composable Ad hoc Mobile Services for Universal Interaction,'' \\
\>\>       3rd ACM/IEEE International Conference on Mobile Computing,  \\
\>\>        Budapest, Hungary, September 1997, pp. 1-12. \\
\>\>        {\em Best Paper award. }\\
\smallskip \\[-3pt]
\>    T. D. Hodes \\
\>\>      ``Recursive Oscillators on a Fixed-Point Vector Microprocessor \\
\>\>\>     for High Performance Additive Synthesis of Audio,'' \\
\>\>       MS report, December 1997. also, UCB Technical Report CSD/98/1007. \\
\smallskip \\[-3pt]
\>    R. H. Katz, E. A. Brewer, E. Amir, H. Balakrishnan, A. Fox,
       S. Gribble, T. Hodes, \\
\>\>\>   D. Jiang, G. Nguyen, V. Padmanabhan, M. Stemm. \\
\>\> ``The Bay Area Research Wireless Access Network (BARWAN),''  \\
\>\> 41st IEEE Computer Society International Conference (COMPCON), 1996. \\
\smallskip \\
\>	W. T. Fennell, Jr., T. Hodes, S. Witherell, C. Goebel, 
	R. Thakkar, T. Schwenk, \\
\>\>	``Method of Managing Multi-Player Game Playing Over a Network,''  \\
\>\>	Patent \#5,695,400: BoxerJAM Films, Charlottesville, Virginia 
(filed 1/96, accepted 12/97).  \\
\smallskip \\
\>    T. D. Hodes, B. A. McCoy, G. Robins \\
\>\>  ``Dynamically Wiresized Elmore-Based Routing Constructions,''  \\
\>\>   1994 IEEE International Symposium on Circuits and Systems, \\
\>\>   London, England, May 1994, Volume I, pp. 463-466. \\
\smallskip \\
\>  T. D. Hodes \\
\>\> ``A Routing Algorithm to Increase the Speed of VLSI Circuits,'' \\
\>\>       Undergraduate Thesis, University of Virginia, \\
\>\>       Charlottesville, Virginia, May 1994. 
\end{tabbing}
\newpage
%\begin{bf} \large
%Publications, cont.
%%\end{bf}
%\begin{tabbing}
%xxi \= xx \= x \= \kill
%\end{tabbing}

\bigskip

\begin{bf} \large
Work Experience
\end{bf}
\medskip

\begin{tabular}{p{5.2in}@{\hspace{1.5cm}}l}
    \em Graduate Student Researcher, UC Berkeley Computer Science division
                                                                 & 1995- \\
       Work on mobile computing \& location-based applications 
       [WINET99, USITS99, PersComm98]; 
       multimedia networking [CompSurveys99, MMCN99];
       peer-to-peer service location [Mobicom99];
       fast sine synthesis techniques with vector instruction 
       sets [ICASSP99] \\[9pt]

    \em Technical Staff, Luxxon corporation, San Jose, California. & 2000-2001 \\
       Worked one day a week assisting with R\&D, especially
       protocols for discovery/negotiation of client
       device characteristics and media caching \\[9pt]

    \em Graduate Internship and Contracting, IBM Almaden Research Center, 
          Almaden, California
                                                              & 1999-2000 \\
       Summer internship and follow-up continuing work with
       the TSpaces middleware project [IECON99] \\[9pt]

    \em Graduate Student Instructor, UC Berkeley Computer Science division
                                                                 & Fall 1996 \\
       Teaching Assistant for {\em Computer Architecture and
       Engineering} (CS152), taught by David Patterson and
       Robert Yung \\[9pt]

    \em BoxerJam Films, Charlottesville, Virginia                & 1994 \\
       Assisted the early-stage design and implementation of 
       a multi-platform
       client/server system communicating via both modems and IP
       networks.  Addressed wide-area latency-hiding and user interface
       issues.  The resulting game, "Strike-A-Match,"
       can be played on America Online (AOL) and Yahoo! 
       [Patent \#5,695,400] \\[9pt]

    \em Unix Consultant, U. of Virginia Information, 
         Technology, and Communications  (ITC)              & 1993-1994 \\
       Answered questions via phone dealing with issues on all the
       University's available UNIX platforms, including SunOS,
       AIX, IRIX, and NeXT \\[9pt]

    \em HBO \& Company, Advanced Technologies Group, 
           Atlanta, Georgia                                      & 1991,1993 \\
       Designed and implemented interfaces and utilities to
       assist integrating PC-based client machines with their
       legacy mainframe (MV/40000) medical system. \\[9pt]

   \em Computer Lab Consultant, U. of Virginia  
      Darden Graduate School of Business Administration          & 1991-1993 \\
       Acted as consultant for lab with DOS/Windows and
       Macintosh machines connected to the campus networks. \\[9pt]

    \em Private Tutor, Atlanta, Georgia                          & 1989-1991 \\
       Tutored local community college students in mathematics
       and the sciences. \\[9pt]

    \em College Bound, Atlanta, Georgia                          & 1988-1990 \\
       Tutored students preparing for the SAT, ACT, SSAT,
       and school classes; maintained accounting records;
       developed/edited software (in BASIC) to score tests and evaluate 
       students. \\[9pt]
\end{tabular}



\end{document}



